paper

### 2024-09-14 paper.qmd
.

# Plot using ggplot2
ggplot(plot_data.melt, aes(x = Alpha, y = FDR, color = Method)) +
  geom_line( size = 1) +
  theme_minimal() +
  labs(title = "Significant Proteins vs FDR",
       x = "FDR",
       y = "Number of Significant Proteins") +
   geom_vline(xintercept = 0.01, linetype="dotted", 
                color = "red", size=1) + 
    geom_vline(xintercept = 0.05, linetype="dotted", 
                color = "red", size=1)+
    scale_color_npg() + 
    theme(
    plot.title = element_text(face = "bold", color = "black"),
    axis.title = element_text(face = "bold", color = "black"),
    axis.text = element_text(face = "bold", color = "black"),
    axis.ticks = element_line(color = "black")
  )
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("UPS1.Case4")
data <- assay(UPS1.Case4)
formula.str <- "~ 0 + Conc. + tool + fake.batch"
meta.info <- data.frame(colData(UPS1.Case4), check.names = FALSE, row.names = row.names(colData(UPS1.Case4)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("Conc.1-Conc.2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="Conc.1-Conc.2" , number = "Inf")
saveRDS(limma.result, "../LimROTS paper/UPS1.Case2.limma.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE}
formula.str <- "~ Conc. + tool + fake.batch"
data("UPS1.Case4")
data <- assay(UPS1.Case4)
meta.info <- data.frame(colData(UPS1.Case4), check.names = FALSE, row.names = row.names(colData(UPS1.Case4)))
meta.info$sample.id <- NULL
ancova.result <- data.frame()
for(i in 1:nrow(data)){
  df.temp <- data[i,]
  data.temp <- data.frame(response = as.numeric(df.temp) , Conc. = meta.info$Conc.,
                     tool = meta.info$tool, fake.batch = meta.info$fake.batch )
  ancova_model <- lm(formula(paste("response", formula.str)), data = data.temp)
  coef_table <- anova(ancova_model)
  coef_table <- data.frame(coef_table)
  significant_groups <- coef_table[rownames(coef_table) == "Conc." , ]
  ancova.result <- rbind(ancova.result, data.frame(protein = row.names(data)[i], p.value =significant_groups[, 5] ))
}
ancova.result$FDR <- p.adjust(ancova.result$p.value, method = "fdr")

@@

@@

predictions_limma <- limma.result$adj.P.Val < 0.01
predictions_limma <- factor(predictions_limma, levels = c(TRUE, FALSE))
true_labels_limma <- ifelse(row.names(limma.result) %in% TP , TRUE, FALSE)
true_labels_limma <- factor(true_labels_limma, levels = c(TRUE, FALSE))
true_labels_limma <- confusionMatrix(predictions_limma, true_labels_limma)

@@

ggplot(all_metrics, aes(x = Metric, y = Value, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_bw() +
  labs(title = "Comparison of Performance Metrics",
       y = "Value", x = "Metric") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

# Plot using ggplot2
ggplot(plot_data.melt, aes(x = Alpha, y = FDR, color = Method)) +
  geom_line( size = 1) +
  theme_minimal() +
  labs(title = "Significant Proteins vs FDR Case study 1",
       x = "FDR",
       y = "Number of Significant Proteins") +
   geom_vline(xintercept = 0.01, linetype="dotted", 
                color = "red", size=1) + 
    geom_vline(xintercept = 0.05, linetype="dotted", 
                color = "red", size=1)+
    scale_color_npg() + 
    theme(
    plot.title = element_text(face = "bold", color = "black"),
    axis.title = element_text(face = "bold", color = "black"),
    axis.text = element_text(face = "bold", color = "black"),
    axis.ticks = element_line(color = "black")
  )
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE, eval=FALSE}

@@

```{r results = "hide" , message = FALSE, warning = FALSE, eval=FALSE}
library(limma)
library(SummarizedExperiment, quietly = T, warn.conflicts = T)
data("UPS1.Case4")
data <- assay(UPS1.Case4)
formula.str <- "~ 0 + Conc. + tool + fake.batch"
meta.info <- data.frame(colData(UPS1.Case4), check.names = FALSE, row.names = row.names(colData(UPS1.Case4)))
meta.info$sample.id <- NULL
design.matrix <- model.matrix(formula(formula.str), data = meta.info)
colnames(design.matrix) <- make.names(colnames(design.matrix))
fit <- lmFit(data, design.matrix)
cont_matrix <- makeContrasts("Conc.1-Conc.2",  levels=design.matrix)
fit2 <- contrasts.fit(fit, cont_matrix)
fit.ebayes <- eBayes(fit2, trend=TRUE, robust=TRUE)
limma.result <- topTable(fit.ebayes, coef="Conc.1-Conc.2" , number = "Inf")
saveRDS(limma.result, "../LimROTS paper/UPS1.Case2.limma.rds")
```

@@

```{r results = "hide" , message = FALSE, warning = FALSE, eval=FALSE}
formula.str <- "~ Conc. + tool + fake.batch"
data("UPS1.Case4")
data <- assay(UPS1.Case4)
meta.info <- data.frame(colData(UPS1.Case4), check.names = FALSE, row.names = row.names(colData(UPS1.Case4)))
meta.info$sample.id <- NULL
ancova.result <- data.frame()
for(i in 1:nrow(data)){
  df.temp <- data[i,]
  data.temp <- data.frame(response = as.numeric(df.temp) , Conc. = meta.info$Conc.,
                     tool = meta.info$tool, fake.batch = meta.info$fake.batch )
  ancova_model <- lm(formula(paste("response", formula.str)), data = data.temp)
  coef_table <- anova(ancova_model)
  coef_table <- data.frame(coef_table)
  significant_groups <- coef_table[rownames(coef_table) == "Conc." , ]
  ancova.result <- rbind(ancova.result, data.frame(protein = row.names(data)[i], p.value =significant_groups[, 5] ))
}
ancova.result$FDR <- p.adjust(ancova.result$p.value, method = "fdr")
saveRDS(ancova.result, "../LimROTS paper/UPS1.Case2.ancova.rds")
```

@@

limrots.result <- readRDS("../LimROTS paper/UPS1.Case2.LimROTS.rds")
limma.result <- readRDS("../LimROTS paper/UPS1.Case2.limma.rds")
ancova.result <- readRDS("../LimROTS paper/UPS1.Case2.ancova.rds")

@@

@@

ggplot(all_metrics, aes(x = Metric, y = Value, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_bw() +
  labs(title = "Comparison of Performance case study 2",
       y = "Value", x = "Metric") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
      scale_fill_npg() + 
    theme(
    plot.title = element_text(face = "bold", color = "black"),
    axis.title = element_text(face = "bold", color = "black"),
    axis.text = element_text(face = "bold", color = "black"),
    axis.ticks = element_line(color = "black")
  )
```
